---
title: "Simulating data with synthpop"
author: "Julia Müller"
date: "31 8 2020"
output: html_document
---

```{r}
library(synthpop)
library(tidyverse)
library(hablar)

df <- read_csv("J:/VS_TillResCorr_Eventstat_ControlTD.csv",
               na = "-")

df %>% 
  group_by(Participant) %>% 
  count()
```

Quick intro to Synthpop: https://synthpop.org.uk/get-started.html

Selecting the variables I want and saving them in df_sim, then the syn command synthesises the new dataset  
The compare function helps compare the old and new datasets  
I took out the participant ID and later put that back in manually, I hope it still works! Something about the combination of either these particular factors or the number of factors generally just threw off the simulation, and I'm not sure why ¯\_(ツ)_/¯
```{r}
df_sim <- df %>% 
  convert(fct(Stimulus, Category.Group, Participant, AOI.Name)) %>% 
  dplyr::select(c(AOI.Name, Trial, Stimulus, Category.Group, Index,
                  Event.Start.Trial.Time, Event.End.Trial.Time, Event.Duration))

mysyn <- syn(df_sim)

compare(mysyn, df_sim)
```

This is a bit roundabout - I can't directly add a variable to a syn object, so I'm exporting it, importing it again, and then adding the participant ID before exporting again
```{r}
write.syn(mysyn, file = "Divya's_sim_data_raw", filetype = "csv")

d <- read_csv("Divya's_sim_data_raw.csv")

d <- d %>% 
  mutate(Participant = c(rep("p1", 1261), 
           rep("p2", 1376),
           rep("p3", 1310),
           rep("p4", 1632),
           rep("p5", 1492),
           rep("p6", 1439),
           rep("p7", 1626),
           rep("p8", 1307),
           rep("p9", 1570),
           rep("p10", 1824),
           rep("p11", 1619),
           rep("p12", 1709),
           rep("p13", 1529),
           rep("p14", 1603),
           rep("p15", 1499),
           rep("p16", 1353),
           rep("p17", 1716),
           rep("p18", 1725),
           rep("p19", 1680),
           rep("p20", 1330),
           rep("p21", 1427),
           rep("p22", 1814)
           ))

write.csv(d, "Divya's_sim_data.csv")
```

